Black swans in ecological time series\\Black swans in population dynamics\\Heavy-tailed ecological time series\\Black swans in ecological dynamics\\Black swan ecological dynamics\\ \ldots

### 2014-10-17 anderson-etal-blackswan-timeseries.tex
Adding to the introduction and discussion;
Edits to the SOM too
Switch back to .tex files; add to SOM
Add a potential title

\title{Black swans in ecological time series\\Black swans in population dynamics\\Heavy-tailed ecological time series\\Black swans in ecological dynamics}
\author{
Sean C. Anderson$^{1\ast}$ \and
Trevor A. Branch$^2$ \and
Andrew B. Cooper$^3$ \and
Nicholas K. Dulvy$^1$
}
\date{}

@@

\setlength\parskip{0.16in}
\setlength\parindent{0in}
\usepackage{titlesec}
\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{-6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{0pt plus 4pt minus 2pt}{-8pt plus 2pt minus 2pt}

@@

\maketitle

@@

\emph{Authors are listed alphabetically (ABCD!) and open to reordering.}

\textsuperscript{1}Earth to ocean research group, department of biological sciences, Simon Fraser University, Burnaby BC, V5A 1S6, Canada

\textsuperscript{2}School of Aquatic and Fishery Sciences, University of Washington, Box 355020, Seattle, WA 98195, USA

\textsuperscript{3}School of Resource and Environmental Management, Simon Fraser University, Burnaby, BC, V5A 1S6, Canada

\textsuperscript{*}Corresponding author: Sean C. Anderson; Earth to Ocean Research Group, Department of Biological Sciences, Simon Fraser University, Burnaby BC, V5A 1S6; Phone: 1-778-782-3989; E-mail: sean\_anderson@sfu.ca

%\begin{spacing}{1.4}
\doublespacing
%\onehalfspacing

@@

\clearpage
\section{Figures}

\input{figs}

>>>>

\title{Black swans in ecological time series\\Black swans in population dynamics\\Heavy-tailed ecological time series\\Black swans in ecological dynamics\\Black swan ecological dynamics\\ \ldots}
\author{
Sean C. Anderson$^{1\ast}$ \and
Trevor A. Branch$^2$ \and
Andrew B. Cooper$^3$ \and
Nicholas K. Dulvy$^1$
}
\date{}

@@

%\setlength\parskip{0.19in}
%\setlength\parindent{0in}
\usepackage{titlesec}
%\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{-6pt plus 2pt minus 2pt}
%\titlespacing\subsection{0pt}{0pt plus 4pt minus 2pt}{-8pt plus 2pt minus 2pt}

@@

\maketitle
\doublespacing
\onehalfspacing

@@

\noindent
\emph{Authors are listed alphabetically (ABCD!) and open to reordering.}

\noindent
\textsuperscript{1}Earth to ocean research group, department of biological sciences, Simon Fraser University, Burnaby BC, V5A 1S6, Canada

\noindent
\textsuperscript{2}School of Aquatic and Fishery Sciences, University of Washington, Box 355020, Seattle, WA 98195, USA

\noindent
\textsuperscript{3}School of Resource and Environmental Management, Simon Fraser University, Burnaby, BC, V5A 1S6, Canada

\noindent
\textsuperscript{*}Corresponding author: Sean C. Anderson; Earth to Ocean Research Group, Department of Biological Sciences, Simon Fraser University, Burnaby BC, V5A 1S6; Phone: 1-778-782-3989; E-mail: sean\_anderson@sfu.ca

%\begin{spacing}{1.4}

%\onehalfspacing

@@
